MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
updates

\begin{abstract}
Despite the security improvements made to Bluetooth since its début in the late 1990s, Bluetooth technology still has many unresolved vulnerabilities that allow for attackers to execute successful Man in the Middle attacks. In particular, the addition of Secure Simple Pairing (SSP) in version 2.1 in 2007
\end{abstract}

>>>>

\begin{abstract}
Despite the security improvements made to Bluetooth since its debut in the late 1990s, Bluetooth technology still has many unresolved vulnerabilities that allow for attackers to execute successful Man in the Middle attacks. In particular, the addition of Secure Simple Pairing (SSP) in version 2.1 in 2007 introduced more security flaws, despite it's purpose to secure the pairing process between devices. This work focuses on launching a successful MiTM attack against a Bluetooth-enabled keyboard and a victim PC and logging the data transmitted from the keyboard to the victim PC. Although there is much work done on MiTM attacks and attacking PIN vulnerabilities, there has been little published research on successfully logging the keystrokes from a Bluetooth keyboard using a MiTM attack. 
\end{abstract}
